Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-20 RR_manuscript/Draft_RR.tex

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g.~Simmons et al.~2011, Gelman \& Loken 2013).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).

While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis.
Analytical approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

@@

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.~Ladd 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch ({\textbf{???}}; Foulkes \& Docherty, 2006; White, Payne, \& Mattys, 2009).

@@

(2a) \enquote{I can't bear ANOTHER meeting on zoom.}
(2b) \enquote{I can't bear another meeting on ZOOM.}

@@

Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
Do we average the domain or do we measure a specific point in time? Do we measure fundamental frequency or intensity? When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes. This plurality of analytical paths is illustrated in figure X. When comparing two utterance such as 2a and 2b, there are many things to consider. Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified. Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint. We could also measure the value or time of the minimum or maximum f0 value. We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0. And the garden of forking paths does not stop here. In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS. Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.

Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

@@

Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

The outcome variable will be the set of standardized effect sizes.
The respective standard errors \(\text{se}_i\) will be included to fit a measurement-error model.
The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight 2000).
The analysis teams will be included as a group-level effect (i.e., random effect).
For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
The code for the model can be found here: INSERT LINK.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-camerer2018evaluating}{}%
Camerer, C. F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} others. (2018). Evaluating the replicability of social science experiments in nature and science between 2010 and 2015. \emph{Nature Human Behaviour}, \emph{2}(9), 637--644. \url{https://doi.org/10.1038/s41562-018-0399-z}

@@

@@

@@

@@

>>>>

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, \& Dubé, 2015; Starns et al., 2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011; Gelman \& Loken, 2014).
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box, 1976; De Groot, 2014; Tukey, 1977).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al., 2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g., Silberzahn et al., 2018; Botvinik-Nezer et al., 2020; Starns et al., 2019).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (``I knew it'', Nickerson, 1998), and perceiving events as being plausible in hindsight (``I knew it all along'', Fischhoff, 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g., Simmons et al., 2011; Gelman \& Loken, 2014).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).

While this issue has been widely discussed both from a conceptual point of view (Nosek \& Lakens, 2014; Simmons et al., 2011; Wagenmakers, Wetzels, Borsboom, Maas, \& Kievit, 2012) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger, 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
Analytical approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

@@

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g., Jongman, Wayland, \& Wong, 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).

@@

(2a) \enquote{I can't bear ANOTHER meeting on zoom.}\\
(2b) \enquote{I can't bear another meeting on ZOOM.}

@@

Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
Do we average the domain or do we measure a specific point in time?
Do we measure fundamental frequency or intensity?
When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
This plurality of analytical paths is illustrated in figure X.
When comparing two utterance such as 2a and 2b, there are many things to consider.
Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
And the garden of forking paths does not stop here.
In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.~????).
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice, 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Rubio-Fernández, 2016; Sedivy, 2003; Westerbeek, Koolen, \& Maes, 2015), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts, Maes, Noordman, \& Jansen, 2011; Paraboni, Van Deemter, \& Masthoff, 2007; Rubio-Fernández, 2016).
Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
For example, Degen, Hawkins, Graf, Kreiss, and Goodman (2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
This account, however, has mainly focused on content selection (Gatt, Gompel, Deemter, \& Krahmer, 2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.

Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd, 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

@@

Assuming that the underlying distribution of effect sizes is normal (Knight, 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

The outcome variable will be the set of standardized effect sizes.
The respective standard errors \(\text{se}_i\) will be included to fit a measurement-error model.
The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight, 2000).
The analysis teams will be included as a group-level effect (i.e., random effect).
For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, Simpson, \& Betancourt, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2018).
The code for the model can be found here: INSERT LINK.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-arts2011overspecification}{}%
Arts, A., Maes, A., Noordman, L. G., \& Jansen, C. (2011). Overspecification in written instruction. \emph{Linguistics}, \emph{49}(3), 555--574.

\leavevmode\hypertarget{ref-botvinik2020variability}{}%
Botvinik-Nezer, R., Holzmeister, F., Camerer, C. F., Dreber, A., Huber, J., Johannesson, M., \ldots{} others. (2020). Variability in the analysis of a single neuroimaging dataset by many teams. \emph{Nature}, 1--7.

\leavevmode\hypertarget{ref-box1976science}{}%
Box, G. E. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799.

\leavevmode\hypertarget{ref-brms}{}%
Bürkner, P.-C. (2018). Advanced Bayesian multilevel modeling with the R package brms. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}

\leavevmode\hypertarget{ref-camerer2018evaluating}{}%
Camerer, C. F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} others. (2018). Evaluating the replicability of social science experiments in nature and science between 2010 and 2015. \emph{Nature Human Behaviour}, \emph{2}(9), 637--644. \url{https://doi.org/10.1038/s41562-018-0399-z}

\leavevmode\hypertarget{ref-degen2020redundancy}{}%
Degen, J., Hawkins, R. D., Graf, C., Kreiss, E., \& Goodman, N. D. (2020). When redundancy is useful: A bayesian approach to ``overinformative'' referring expressions. \emph{Psychological Review}.

\leavevmode\hypertarget{ref-de2014thought}{}%
De Groot, A. D. (2014). \emph{Thought and choice in chess} (Vol. 4). Walter de Gruyter GmbH \& Co KG.

@@

\leavevmode\hypertarget{ref-fischhoff1975hindsight}{}%
Fischhoff, B. (1975). Hindsight is not equal to foresight: The effect of outcome knowledge on judgment under uncertainty. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{1}(3), 288.

@@

\leavevmode\hypertarget{ref-gatt2013we}{}%
Gatt, A., Gompel, R. P. van, Deemter, K. van, \& Krahmer, E. (2013). Are we bayesian referring expression generators. In. Cognitive Science Society.

\leavevmode\hypertarget{ref-gelman2014statistical}{}%
Gelman, A., \& Loken, E. (2014). The statistical crisis in science: Data-dependent analysis--a" garden of forking paths"--explains why many statistically significant comparisons don't hold up. \emph{American Scientist}, \emph{102}(6), 460--466.

\leavevmode\hypertarget{ref-Gelman_2017}{}%
Gelman, A., Simpson, D., \& Betancourt, M. (2017). The prior can often only be understood in the context of the likelihood. \emph{Entropy}, \emph{19}(10), 1--13. \url{https://doi.org/10.3390/e19100555}

\leavevmode\hypertarget{ref-gordon2017acoustic}{}%
Gordon, M., \& Roettger, T. (2017). Acoustic correlates of word stress: A cross-linguistic survey. \emph{Linguistics Vanguard}, \emph{3}(1), 1--11.

\leavevmode\hypertarget{ref-grice1975logic}{}%
Grice, H. P. (1975). Logic and conversation. In \emph{Speech acts} (pp. 41--58). Brill.

\leavevmode\hypertarget{ref-hawkins2004influence}{}%
Hawkins, S., \& Nguyen, N. (2004). Influence of syllable-coda voicing on the acoustic properties of syllable-onset /l/ in English. \emph{Journal of Phonetics}, \emph{32}(2), 199--231.

\leavevmode\hypertarget{ref-jongman2000acoustic}{}%
Jongman, A., Wayland, R., \& Wong, S. (2000). Acoustic characteristics of english fricatives. \emph{The Journal of the Acoustical Society of America}, \emph{108}(3), 1252--1263.

\leavevmode\hypertarget{ref-knight2000}{}%
Knight, K. (2000). \emph{Mathematical statistics}. Chapman; Hall, New York.

\leavevmode\hypertarget{ref-koole2012rewarding}{}%
Koole, S. L., \& Lakens, D. (2012). Rewarding replications: A sure and simple way to improve psychological science. \emph{Perspectives on Psychological Science}, \emph{7}(6), 608--614.

\leavevmode\hypertarget{ref-ladd2008intonational}{}%
Ladd, D. R. (2008). \emph{Intonational phonology}. Cambridge University Press.

@@

\leavevmode\hypertarget{ref-lisker1977rapid}{}%
Lisker, L. (1977). Rapid versus rabid: A catalogue of acoustic features that may cue the distinction. \emph{The Journal of the Acoustical Society of America}, \emph{62}(S1), S77--S78.

\leavevmode\hypertarget{ref-lisker1986voicing}{}%
Lisker, L. (1986). ``Voicing'' in English: A catalogue of acoustic features signaling /b/ versus /p/ in trochees. \emph{Language and Speech}, \emph{29}(1), 3--11.

\leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
Nickerson, R. S. (1998). Confirmation bias: A ubiquitous phenomenon in many guises. \emph{Review of General Psychology}, \emph{2}(2), 175--220.

\leavevmode\hypertarget{ref-nosek2014method}{}%
Nosek, B. A., \& Lakens, D. (2014). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137--141.

\leavevmode\hypertarget{ref-ogden2004}{}%
Ogden, R. (2004). Non-modal voice quality and turn-taking in Finnish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.

@@

\leavevmode\hypertarget{ref-paraboni2007generating}{}%
Paraboni, I., Van Deemter, K., \& Masthoff, J. (2007). Generating referring expressions: Making referents easy to identify. \emph{Computational Linguistics}, \emph{33}(2), 229--254.

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-roettger2019researcher}{}%
Roettger, T. B. (2019). Researcher degrees of freedom in phonetic research. \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology}, \emph{10}(1).

\leavevmode\hypertarget{ref-rotello2015more}{}%
Rotello, C. M., Heit, E., \& Dubé, C. (2015). When more data steer us wrong: Replications with the wrong dependent measure perpetuate erroneous conclusions. \emph{Psychonomic Bulletin \& Review}, \emph{22}(4), 944--954.

\leavevmode\hypertarget{ref-rubio2016redundant}{}%
Rubio-Fernández, P. (2016). How redundant are redundant color adjectives? An efficiency-based analysis of color overspecification. \emph{Frontiers in Psychology}, \emph{7}, 153.

\leavevmode\hypertarget{ref-sedivy2003pragmatic}{}%
Sedivy, J. C. (2003). Pragmatic versus form-based accounts of referential contrast: Evidence for effects of informativity expectations. \emph{Journal of Psycholinguistic Research}, \emph{32}(1), 3--23.

\leavevmode\hypertarget{ref-silberzahn2018many}{}%
Silberzahn, R., Uhlmann, E. L., Martin, D. P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others. (2018). Many analysts, one data set: Making transparent how variations in analytic choices affect results. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337--356.

\leavevmode\hypertarget{ref-simmons2011false}{}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2011). False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant. \emph{Psychological Science}, \emph{22}(11), 1359--1366.

\leavevmode\hypertarget{ref-stan}{}%
Stan Development Team. (2019). Stan modeling language users guide and reference manual (Version 2.18.0). Stan Development Team. Retrieved from \url{http://mc-stan.org}

\leavevmode\hypertarget{ref-starns2019assessing}{}%
Starns, J. J., Cataldo, A. M., Rotello, C. M., Annis, J., Aschenbrenner, A., Bröder, A., \ldots{} Wilson, J. (2019). Assessing theoretical conclusions with blinded inference to investigate a potential inference crisis. \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 335--349.

\leavevmode\hypertarget{ref-sterling1959publication}{}%
Sterling, T. D. (1959). Publication decisions and their possible effects on inferences drawn from tests of significance---or vice versa. \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
